Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-12 Paper.Rmd

\begin{figure}[!h]
\textbf{ \hspace{6 cm} (A) \hspace{6 cm} (B)} \\
\vspace{-0.1 cm}
\begin{center}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_spearman.pdf}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_spearman.pdf}\\
\end{center}
\vspace{0.2 cm}
\textbf{ \hspace{6 cm} (C) \hspace{6 cm} (D)} \\
\vspace{-0.1 cm}
\begin{center}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_spearman.pdf}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_methane/skewness_methane_spearman.pdf}
\caption{Skewness of spatially averaged green spruce aphid abundance $(A)$, leaf-curling plum 
aphid first flight dates $(B)$, \emph{Ceratium furca} abundance $(C)$, and methane-flux
$(D)$ time series compared to an multivariate 
N-copula null hypothesis. Red dots are empirical 
skewnesses; see text 
and Appendix \ref{SM-Surrog_multi} for details of the null hypothesis. Results show a 
tendency for skewness of the spatial average to be affected as hypothesized 
by tail dependence. \label{fig_skewness_spearman}}
\end{center}
\end{figure}
<!--***DAN: Shya, please replace the x axis label by "Skewness" and the y-axis label
by "Frequency" in the above plot-->

>>>>

\begin{figure}[!h]
\textbf{ \hspace{6 cm} (A) \hspace{6 cm} (B)} \\
\vspace{-0.1 cm}
\begin{center}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_spearman.pdf}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_spearman.pdf}\\
\end{center}
\vspace{0.2 cm}
\textbf{ \hspace{6 cm} (C) \hspace{6 cm} (D)} \\
\vspace{-0.1 cm}
\begin{center}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_spearman.pdf}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_methane/skewness_methane_spearman.pdf}
\caption{Skewness of spatially averaged green spruce aphid abundance $(A)$, leaf-curling plum 
aphid first flight dates $(B)$, \emph{Ceratium furca} abundance $(C)$, and methane-flux
$(D)$ time series compared to an multivariate 
N-copula null hypothesis. Black dots are empirical 
skewnesses; see text 
and Appendix \ref{SM-Surrog_multi} for details of the null hypothesis. Results show a 
tendency for skewness of the spatial average to be affected as hypothesized 
by tail dependence. \label{fig_skewness_spearman}}
\end{center}
\end{figure}

### 2019-02-12 SupportingInformation.Rmd

```{r tab_aphid_info, echo=F, results='asis',message=F}
library(tinytex)
library(tibble)
aphid_info <- tibble(c1=c("Apple grass aphid","Bird cherry oat aphid","Black bean aphid","Blackberry cereal aphid","Blackcurrant sowthistle aphid",
                       "Corn leaf aphid","Currant lettuce aphid","Damson hop aphid","Grain aphid","Green spruce aphid",
                       "Leaf-curling plum aphid","Mealy cabbage aphid","Mealy plum aphid","Pea aphid","Peach potato aphid",
                       "Potato aphid","Rose grain aphid","Shallot aphid","Sycamore aphid","Willow carrot aphid"),
                     c2=c("Rhopalosiphum insertum", "Rhopalosiphum padi", "Aphis fabae", "Sitobion fragariae", "Hyperomyzus lactucae",
                       "Rhopalosiphum maidis", "Nasonovia ribisnigri","Phorodon humuli","Sitobion avenae","Elatobium abietinum",
                       "Brachycaudus helichrysi","Brevicoryne brassicae","Hyalopterus pruni","Acyrthosiphon pisum","Myzus persicae",
                       "Macrosiphum euphorbiae","Metopolophium dirhodum","Myzus ascalonicus","Drepanosiphum platanoidis","Cavariella aegopodii")
)
knitr::kable(aphid_info, "latex", booktabs = T, linesep = "",
      caption = "Species names of 20 aphids for which data were available \\label{tab_aphid_info}",
      col.names = c("Common name", "Latin binomial"))
```

>>>>

```{r tab_aphid_info, echo=F, results='asis',message=F}
library(tinytex)
library(tibble)
library(kableExtra)
library(dplyr)
aphid_info <- tibble(c1=c("Apple grass aphid","Bird cherry oat aphid","Black bean aphid","Blackberry cereal aphid","Blackcurrant sowthistle aphid",
                       "Corn leaf aphid","Currant lettuce aphid","Damson hop aphid","Grain aphid","Green spruce aphid",
                       "Leaf-curling plum aphid","Mealy cabbage aphid","Mealy plum aphid","Pea aphid","Peach potato aphid",
                       "Potato aphid","Rose grain aphid","Shallot aphid","Sycamore aphid","Willow carrot aphid"),
                     c2=c("Rhopalosiphum insertum", "Rhopalosiphum padi", "Aphis fabae", "Sitobion fragariae", "Hyperomyzus lactucae",
                       "Rhopalosiphum maidis", "Nasonovia ribisnigri","Phorodon humuli","Sitobion avenae","Elatobium abietinum",
                       "Brachycaudus helichrysi","Brevicoryne brassicae","Hyalopterus pruni","Acyrthosiphon pisum","Myzus persicae",
                       "Macrosiphum euphorbiae","Metopolophium dirhodum","Myzus ascalonicus","Drepanosiphum platanoidis","Cavariella aegopodii")
)

knitr::kable(aphid_info, "latex", booktabs = T, linesep = "",
      caption = "Species names of 20 aphids for which data were available \\label{tab_aphid_info}",
      col.names = NULL)%>%
     column_spec(column = 2,italic=T)%>%add_header_above(header=c("Common name" = 1, "Latin binomial" = 1))
```
